Machine Learning Approach to Soccer Player's Overall Rating Prediction

### 2021-12-09 Paper/main.tex
Update data processing & regression code
- Updated data processing code to drop column "Potential". This is highly correlated to overall rating and is not an objective metric;
- Updated regression code. The data processing part in this code is removed since data has already been processed, and added some plotting code.
- Also added project topic, names and emails into the LaTex file.

%%%% PROJECT TITLE
\title{Your Wonderful Project Topic}

%%%% NAMES OF ALL THE STUDENTS INVOLVED (first-name last-name)
\author{\href{mailto:author1@nyu.edu}{Author \#1}, \href{mailto:author2@nyu.edu}{Author \#2}}

@@

\begin{abstract}
    A abstract sums up your work in very few sentences:
    (i) state the problem you are addressing;
    (ii) say why it’s an interesting problem, and which issues are hard to tackle; 
    (iii) give your approach towards solving the problem; 
    (iv) say Why and how well your approach solves the problem.
\end{abstract}

@@

Your introduction briefly explains the problem you address, and what you’ve achieved towards solving the problem. It’s an edited and updated version of your introduction and objective from your topic proposal

@@

Now we beginning the data processing.
There are 18206 players for which 89 features each are provided. Firstly, we should drop the duplicate entries. 
Then we check the variables: 
\begin{center}
$ID, Name, Age, Photo, Nationality, Flag, Overall, Potential, Club, Club Logo, Value,$\\ 
$Wage, Special, Preferred Foot, International Reputation, Weak Foot, Skill Moves,$\\
$Work Rate, Body Type, Real Face, Position, Jersey Number, $\\
$Joined, Loaned From, Contract Valid Until,Height, Weight,$\\
$LS, ST, RS, LW, LF, CF, RF, RW, LAM, CAM, RAM, LM, LCM, CM,$\\
$RCM, RM, LWB, LDM, CDM, RDM, RWB, LB, LCB, CB, RCB, RB,$ \\
$Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys, Dribbling,$\\ 
$Curve, FKAccuracy, LongPassing, BallControl, Acceleration,$\\ 
$SprintSpeed, Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength,$\\ $LongShots, Aggression, Interceptions, Positioning, Vision, Penalties, Composure,$\\ $Marking, StandingTackle, SlidingTackle,$\\
$GKDiving, GKHandling, GKKicking, GKPositioning,
GKReflexes, Release Clause$
\end{center}
\\
Now we have to delete the missing value which will distrubing our model.

@@

Considering these missing value we have below comments:
\begin{itemize}
    \item Since a big chunk of players are not loaned to other clubs, hence there are $16943$ missing values out of $18206$ i.e. they play for their own club.
    \item There is a consistency $(11.45\%)$ in missing values for the position (they play on), this needs to be explored.
    \item Release clause, joined, contract valid until, club, position, jersey number have missing values and need to be explored.
    \item There is a consistency $(0.26\%)$ in missing values for the players rating attributes.
\end{itemize}
\\
Now we will drop unnecessary columns, which can address the problem simply, reference the FIFA official guideline (https://www.fifauteam.com/fifa-19-attributes-guide/). we only keep significant values that have highly contributed to the model.

>>>>

%%%% PROJECT TITLE
\title{Machine Learning Approach to Soccer Player's Overall Rating Prediction}

%%%% NAMES OF ALL THE STUDENTS INVOLVED (first-name last-name)
\author{\href{mailto:ao2186@nyu.edu}{Antai Ouyang \#1}, \href{mailto:xl3215@nyu.edu}{Xianglong Li \#2}, \href{mailto:hl4151@nyu.edu}{Haochen Li \#3}}

@@

\begin{abstract}
    A abstract sums up your work in very few sentences:
    (i) state the problem you are addressing;
    (ii) say why it's an interesting problem, and which issues are hard to tackle; 
    (iii) give your approach towards solving the problem; 
    (iv) say Why and how well your approach solves the problem.
\end{abstract}

@@

Your introduction briefly explains the problem you address, and what you've achieved towards solving the problem. It's an edited and updated version of your introduction and objective from your topic proposal

@@

Now we beginning the data processing.
There are 18206 players for which 89 features each are provided. Firstly, we should drop the duplicate entries. 
Then we check the variables: 
\begin{center}
$ID, Name, Age, Photo, Nationality, Flag, Overall, Potential, Club, Club Logo, Value,$\\ 
$Wage, Special, Preferred Foot, International Reputation, Weak Foot, Skill Moves,$\\
$Work Rate, Body Type, Real Face, Position, Jersey Number, $\\
$Joined, Loaned From, Contract Valid Until,Height, Weight,$\\
$LS, ST, RS, LW, LF, CF, RF, RW, LAM, CAM, RAM, LM, LCM, CM,$\\
$RCM, RM, LWB, LDM, CDM, RDM, RWB, LB, LCB, CB, RCB, RB,$ \\
$Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys, Dribbling,$\\ 
$Curve, FKAccuracy, LongPassing, BallControl, Acceleration,$\\ 
$SprintSpeed, Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength,$\\ $LongShots, Aggression, Interceptions, Positioning, Vision, Penalties, Composure,$\\ $Marking, StandingTackle, SlidingTackle,$\\
$GKDiving, GKHandling, GKKicking, GKPositioning,
GKReflexes, Release Clause$
\end{center}
\par Now we have to delete the missing value which will distrubing our model.

@@

Considering these missing value we have below comments:
\begin{itemize}
    \item Since a big chunk of players are not loaned to other clubs, hence there are $16943$ missing values out of $18206$ i.e. they play for their own club.
    \item There is a consistency $(11.45\%)$ in missing values for the position (they play on), this needs to be explored.
    \item Release clause, joined, contract valid until, club, position, jersey number have missing values and need to be explored.
    \item There is a consistency $(0.26\%)$ in missing values for the players rating attributes.
\end{itemize}
\par Now we will drop unnecessary columns, which can address the problem simply, reference the FIFA official guideline (https://www.fifauteam.com/fifa-19-attributes-guide/). we only keep significant values that have highly contributed to the model.
